R Notebook

### 2020-10-07 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
Startet på analyse, la inn datautvalget.

```{r setup, echo=FALSE}

```

>>>>

```{r setup, echo = FALSE}
library(modelr)
library(ggplot2)
library(knitr)
library(tinytex)
library(tidyverse)
library(ggpubr)
library(dplyr)
```

## Introduksjon

## Analyse

Vi starter ved å vise utvalget i datasettet for å gi en oversikt:

```{r Datautvalg sortert, echo=FALSE}
heights$heightInt <- cut(heights$height, breaks = 8)
kable(summary(heights[,1:4]))
kable(summary(heights[,5:9]))
```

## Referanser
